\chapter{Conclusion and Future Work} \label{cha:conclusion}
This work aimed to design and implement REST API, which exposes the reservation system Shongo's back-end (Controller module) to higher layers.

In conclusion, this work implemented a new functional API fulfilling REST principles for the Shongo system.
As a result, the new front-end \cite{drobnakm} can interact with the Shongo back-end, thus making the original \texttt{shongo-web-client} module obsolete. However, this functionality was tested just locally since the deployment was out of the scope of this thesis.
Moreover, the API makes the Shongo system available for any application or service outside of the Shongo system.

The resulting REST API is documented with \texttt{Javadoc}, and the OpenAPI specification (\Cref{sec:openapi}) is generated and made available on the REST server.
In addition, this specification is added to Spring UI (\Cref{sec:swagger}), which is also deployed on the REST server.

And what are the following plans after this thesis?
First and foremost, the implementation of REST API has to be deployed, and the functionality of the REST server with the new front-end has to be adequately tested, first on the development server and eventually on the \emph{meetings server}\footnote{\url{https://meetings.cesnet.cz/}}.
Additionally, the implementation of run-time management endpoints should be fine-tuned after deploying the new front-end.
Finally, the next step could be more complex connections between Shongo exceptions and REST API \texttt{ExceptionHandler}.
