\chapter{Implementation and Documentation} \label{cha:implementation}
All classes related to the REST API are stored in the Controller’s package  \texttt{cz.cesnet.shongo.controller.rest}.
Aside from this package, the only changes made are in a few files that retrieve data from the database --- where additional data were required to be loaded --- and inter-domain implementation files\cite{pavelka2016shongo} whose configuration has been merged with the REST configuration.

\section{REST Server}
The cornerstone of the implementation is the REST server which listens for incoming HTTP requests from clients and responds to them in the desired way. The REST server is implemented in the \texttt{RESTApiServer} class.
At the start of the \emph{Controller} service, the REST server is attached to the \emph{Controller}.

\texttt{RESTApiServer} starts a \emph{Jetty}\footnote{\url{https://www.eclipse.org/jetty/}} server and configures it according to the controller configuration. The server then listens on the host and port specified in the configuration.

\section{Configuration}
The REST server configuration is required before implementing API endpoints. These configuration files are stored in the \texttt{config} sub-package.

\subsection{Configuration File Extension}
First, the configuration of the REST server itself is essential. The controller configuration file \texttt{shongo-controller.cfg.xml} has been extended with the parameterization for the new code. Consequently, Shongo administrators can set the REST API server properties inside the \texttt{<rest-api>} XML element. An example of this new configuration is shown in \Cref{conf}. There are several configurable sub elements:
\begin{itemize}
    \item \texttt{<host>} -- the host where the REST API shall serve
    \item \texttt{<port>} -- the port where the REST API shall serve
    \item \texttt{<origin>} -- the allowed origins for the REST API CORS configuration
    \item \texttt{<ssl-key-store>} -- the SSL (Secure Socket Layer) key store from inter-domain extension \cite{pavelka2016shongo}
    \item \texttt{<ssl-key-store-type>} -- the type of key store
    \item \texttt{<ssl-key-store-password>} -- the password for key store
\end{itemize}

\begin{lstlisting}[language=XML, caption=REST configuration example, label=conf]
<?xml version="1.0" encoding="UTF-8" ?>
<configuration>
    ...
    <rest-api>
        <host>meetings.cesnet.cz</host>
        <port>9999</port>
        <origin>http://localhost:4200</origin>
        <origin>https://meetings.cesnet.cz</origin>
        <ssl-key-store>keystore/server.keystore</ssl-key-store>
        <ssl-key-store-password>
            (password)
        </ssl-key-store-password>
    </rest-api>
    ...
</configuration>
\end{lstlisting}

\subsection{Security}
Next, the security and authentication had to be configured. For this purpose, \emph{Spring security} is used. Spring security dependencies have been added to \emph{Controller}'s \texttt{pom.xml}, and security configuration files were stored in \texttt{config.security} sub-package.

The web security is configured in the \texttt{SecurityConfig} class annotated with the Spring \texttt{@EnableWebSecurity} annotation, which allows this class to configure web security\cite{springdocumentation}.
This configuration file defines what should happen to the incoming request. The request filters are added to the request processing, and CORS (Cross-Origin Resource Sharing)\footnote{\url{https://www.w3.org/TR/cors/}} is configured here. The paths that should be skipped in the authentication process are also set here. At the moment, these include OpenAPI, Swagger, inter-domain endpoints\cite{pavelka2016shongo}, and endpoints responsible for processing problem reports.

Additionally, \texttt{AuthFilter} is added, which serves as a REST API middleware. It processes each request (omitting those configured in SecurityConfig) using the following steps:
\begin{enumerate}
    \item Decode an access token wrapped in the HTTP request authorization header as a bearer token.
    \item Check the token authorization.
    \item Convert the token into \texttt{SecurityToken} object which contains an \emph{access token} for Shongo Controller and cached information about the user to whom the token belongs.
    \item Add this new object to the request attributes using the \texttt{TOKEN} key so that subsequent endpoint handling (next middleware or final method) can effortlessly work with it.
\end{enumerate}
If the token is not present or is invalid, the server responds with an HTTP \emph{401 UNAUTHORIZED} response code.

\section{REST Controllers}
This section uses information from Spring documentation \cite{springdocumentation}.
The REST Controllers are responsible for operating the API endpoints and are stored in the \texttt{controllers} sub-package. An example of such a Controller can be observed in \Cref{lst:controller}.

The REST Controllers are annotated with \texttt{@RestController} annotation from the Spring framework, which combines two other annotations:
\begin{description}
    \item \texttt{@Controller} -- makes the class auto-detectable through classpath scanning
    \item \texttt{@ResponseBody} -- binds the return values of the mapped methods to the HTTP response body
\end{description}
This annotation is combined with the \texttt{@RequestMapping} annotation, which uses the web request path to map the incoming request to the method that processes the request and responds to the client. \texttt{@RequestMapping} can also be parameterized, particularly with \texttt{path} (path to the endpoint), \texttt{consumes} (expected incoming body form), and \texttt{produces} (outgoing body form) parameters.

There are usually only few attributes in the controller classes. These attributes are generally Controller’s services, and \emph{dependency injection} is used to access these services. Thanks to Spring annotation \texttt{@Autowired}, they are resolved to \emph{Beans} defined in \texttt{rest-api-servlet.xml} and injected into the controller class. The example of this file can be noticed in \Cref{lst:beans}.

\begin{lstlisting}[language=XML, caption=rest-api-servlet.xml, label=lst:beans]
<?xml version="1.0" encoding="UTF-8"?>
<beans xmlns=
"http://www.springframework.org/schema/beans"
       ...>
    <context:component-scan base-package="cz.cesnet.shongo.controller"/>
    <mvc:annotation-driven />
    <aop:aspectj-autoproxy />
    
    <bean id="controller" class=
    "cz.cesnet.shongo.controller.Controller" factory-method="getInstance"/>
    <bean id="configuration" factory-bean="controller" factory-method="getConfiguration"/>
    <bean id="controllerClient" class=
    "cz.cesnet.shongo.controller.ControllerClient">
        <constructor-arg>
            <bean factory-bean="configuration" factory-method="getRpcUrl"/>
        </constructor-arg>
    </bean>
    <bean id="controllerReservationService" factory-bean="controllerClient" factory-method="getService">
        <constructor-arg value=
        "cz.cesnet.shongo.controller.api.rpc.
        ReservationService" type="java.lang.Class"/>
    </bean>
    ...
    <bean id="cache" class=
    "cz.cesnet.shongo.controller.rest.Cache"/>
</beans>
\end{lstlisting}

The last part of REST Controllers is the declaration and implementation of methods handling distinct REST resources. The methods are annotated with \texttt{@RequestMapping} or rather an exact mapping according to the selected HTTP method (\texttt{@GetMapping}, \texttt{@PostMapping}, \texttt{@PutMapping}, \texttt{@DeleteMapping}).
These annotations also take a path parameter, which is then concatenated to the class’s \texttt{@RequestMapping} path parameter.
In addition, the methods can retrieve HTTP request attributes annotated with \texttt{@RequestAttribute} (most importantly SecurityToken added by \texttt{AuthFilter}), HTTP request parameters annotated with \texttt{@RequestParam}, path parameters annotated with \texttt{@PathVariable} (and specified in the path as \texttt{"\{variableName\}"}) and also the request body annotated with \texttt{@RequestBody}.

\input{assets/controller}

\section{Data Models}
Model classes are mostly POJOs (Plain Old Java Objects) that represent objects received or sent by endpoints. The models are stored in the \texttt{models} sub-package. Usually, attributes with getters and setters are the only content of these classes. Therefore, most of them use \texttt{@Data} annotation from the project Lombok (\Cref{sec:lombok}).
\emph{Jackson} can then serialize and deserialize these classes as described in \Cref{sec:jackson}. Attributes not eligible for serialization are annotated with \texttt{@JacksonIgnore} and for custom name of field in serialized object \texttt{@JacksonProperty("field\_name")} is used.
That does not mean that these classes cannot include anything else. Most importantly, they usually also contain \texttt{fromApi()} and \texttt{toApi()} methods which serve as converters from and to Controller API objects. The \Cref{lst:model} serves as an example of such class.

\begin{lstlisting}[language=java, caption=RoomModel.java, label=lst:model]
// Generates constructor, getters, setters, equals, and hashCode functions
// These generated functions enables Jackson to (de)serialize this object
@Data
// Represents Controller's executable
public class RoomModel {

    // Ignores this attribute during (de)serialization
    @JacksonIgnore
    private Cache cache;

    private String id;
    private ExecutableSummary.Type type;
    private TimeInterval slot;
    private TechnologyModel technology;
    private RoomState state;
    // (De)serializes this attribute to license_count field
    @JsonProperty(license_count)
    private int licenceCount;
    ...

    // Creates this object from data acquired from Controller service
    public static RoomModel fromApi(ExecutableSummary summary)
    {
        RoomModel roomModel = new RoomModel();
        roomModel.setId(summary.getId());
        roomModel.setType(summary.getType());
        roomModel.setSlot(new TimeInterval(summary.getSlot()));
        roomModel.setState(
                RoomState.fromRoomState(
                        summary.getState(), summary.getRoomLicenseCount(),
                        summary.getRoomUsageState())
        );
        ...
        return roomModel;
    }
}
\end{lstlisting}


\section{Error Handling}
Quite many things can go wrong while processing a request. For this reason, the \texttt{error} sub-package was created for files concerning errors and their handling.
For extraordinary cases, new exceptions were made, such as \texttt{UnsupportedApiException} or \texttt{ObjectInaccessible\-Exception}.
These (and any other) exceptions can be thrown during request processing, in which case, the server responds with HTTP response 500 Internal Server Error and prints the \emph{stacktrace} to the HTTP body by default.
To provide better information for the client, \texttt{GlobalController\-ExceptionHandler} class was implemented and annotated with Spring web annotation \texttt{@RestControllerAdvice}.
The methods in the class are annotated with \texttt{@ExceptionHandler}, which takes an exception as a parameter. If this exception is thrown, the request processing intercepts and the annotated method runs instead.
These methods can handle the exception and then respond to the client with the \texttt{ResponseEntity} object. As a result, any object can be passed into the HTTP response body with a desired HTTP response status code.

\begin{lstlisting}[language=java, caption=GlobalControllerExceptionHandler.java, label=lst:err]
@RestControllerAdvice
public class GlobalControllerExceptionHandler
{
    @ExceptionHandler(TodoImplementException.class)
    public ResponseEntity<String> handleTodo(TodoImplementException e) {
        return ErrorModel.createResponseFromException(e, HttpStatus.NOT_IMPLEMENTED);
    }
    ...
}
\end{lstlisting}


\section{Miscellaneous}
The \texttt{ClientWebUrl} class holds the String constants for the endpoints paths. All REST API endpoints paths have the default prefix --- \texttt{/api/v1}.

\texttt{Cache} and \texttt{CacheProvider} classes supply a simple \emph{cache} for several frequently retrieved entities represented by \texttt{ExpirationMap}, which stores the requested entities for a determined amount of time, so the REST API does not have to wait for a much slower database after each request.


\section{Documentation}
The OpenAPI (\Cref{sec:openapi}) specification of the just described implementation of REST API is generated using \texttt{Springdoc} from the Spring framework (\Cref{sec:spring}), so the users can have general and straightforward API documentation available to them.
For this purpose, the \emph{springdoc-openapi} dependency was added to \emph{Controller}'s \texttt{pom.xml}, and the \texttt{OpenApiConfig} class was created. In this configuration file, Springdoc dependencies were imported using Spring's \emph{@Import}, global API attributes were defined with \texttt{@OpenAPIDefinition}, and security was defined with \texttt{@SecurityScheme} annotation.
This is shown in \Cref{lst:openapiconf}.
\begin{lstlisting}[language=Java, caption=OpenApiConfig.java, label=lst:openapiconf]
@Configuration
@EnableWebMvc
@OpenAPIDefinition(
        info = @Info(title = "Shongo API", version = "v1"),
        security = @SecurityRequirement(name = "bearerAuth")
)
@SecurityScheme(
        name = "bearerAuth",
        type = SecuritySchemeType.HTTP,
        scheme = "bearer"
)
@ComponentScan(basePackages = {"org.springdoc"})
@Import({
        SpringDocConfiguration.class,
        SpringDocWebMvcConfiguration.class,
        SwaggerConfig.class,
        SwaggerUiConfigProperties.class,
        SwaggerUiOAuthProperties.class,
        JacksonAutoConfiguration.class
})
class OpenApiConfig implements WebMvcConfigurer {
    ...
}
\end{lstlisting}
Springdoc generates OpenAPI specification based on Spring web annotations by default, but Springdoc annotations such as \texttt{@Operation} or \texttt{@ApiResponses} can customize the resulting specification.
The resulting OpenAPI file is added to the REST server and is available at the \texttt{/v3/open-api} path \cite{springdoc}.

The Swagger UI (\Cref{sec:swagger}) is then used for user-friendly visualization of the OpenAPI specification mentioned above.
The user interface (web site) is acquired and saved in the project resources using the same \emph{springdoc-openapi} dependency as for OpenAPI specification. After that, the default OpenAPI path is set to \texttt{/v3/open-api}. Finally, these resources are added to the REST API server and made available at the \texttt{/swagger-ui/index.html} path.
